\documentclass{article}
\usepackage{graphicx}
\usepackage{parskip}
\usepackage{hyperref}
\usepackage{amsmath}

\begin{document}
\section{General Algebra Problems}

\begin{enumerate}

	\item{Given the equation $\frac{1}{4}v=2+3$, what is the value of $6v-17+18-19+20$ (1)?

	      Answer: 122}
	\item {Given the system of equations:
	      \[
		      \begin{array}{l}
			      \begin{cases}
				      $-2x+by=59$ & \\
				      $5x-y=1$
			      \end{cases}
		      \end{array}\]
	      If the system of equations has exactly one solution $(x,y)$ and $x=2$, what is the value of $b$ (1)?

	      Answer: 7
	      }
	\item {The weight, $w$, in ounces, of a glass soda bottle design with a side length of $l$ inches is given by the equation. By how many ounces does the weight of the bottle increase for every inch of increase in the side length, with the following equation (1)? \[w=3.1 + \frac{l}{2}\]

	      Answer: 0.5}

	\item {The equation $8x-6y=1$ is graphed in the $xy$-plane. What is the slope of the line (1)?

	      Answer: $\frac{4}{3}$}
	\item {Given the system of equations:
	      \[
		      \begin{array}{l}
			      \begin{cases}
				      $-x+3=y$ & \\
				      $-6x+18=6y$
			      \end{cases}
		      \end{array}\]
	      What are the solutions to the equation (1)?

	      Answer: There are infinitely many solutions.
	      }

	\item {Given the equation $C = 290+155h$: A team of painters is hired to paint the exterior of a museum. The total cost, $C$, in dollars, incurred by the museum for $h$ hours of painting is given by the equation. What is the best interpretation of $155$ in the equation (1)?

	      Answer: Each additional hour of painting the exterior costs $\$155$}

	\item {
	      On Monday, Harry had $75\%$ as many toys as Teddy did. On Tuesday, Harry acquires $32$ more toys, and Teddy acquires $15\%$ as many toys as he had on Monday. If Harry and Teddy now have the same number of toys, how many toys did Harry have on Monday (1)?

	      Answer: 60
	      }


	\item {
	      At the beginning of the season, MacDonald had to remove $5$ orange trees from his farm. Each of the remaining trees produced $210$ oranges for a total harvest of $41790$ oranges. If $t$ is the initial number of trees on MacDonald's farm, what equation best describes the situation (1)?

	      Answer: $210(t-5)=41790$
	      }

	\item {
	      To rent a car for one week, a car rental company charges a $\$200$ base price as well as $\$0.45$ per mile. Jennifer will rent a vehicle at this company, but she has a $\$275$ budget. How many miles can Jennifer drive without exceeding her budget (1).

	      Answer: 166 miles
	      }

	\item {
	      A concert venue soltd two teypes of tickets for an upcoming concert: reserved tickets and general admission tickets. Reserved tickets sold for $\$50.00$, and general admission tickets sold for $\$34.00$ each. If $1520$ tickets were sold for a total of $\$64000$, what is a system of equations that could be used to find the number of reserved tickets, $r$, and the number of general admission tickets $g$, that were sold (1)?

	      Answer:
	      \[
		      \begin{array}{l}
			      \begin{cases}
				      $50r+34g=64000$ & \\
				      $r+g=1520$
			      \end{cases}
		      \end{array}\]
	      }
	\item {A line is graphed in the $xy$ plane. What is the equation of the line (1)?

	      Answer choices:
	      \begin{enumerate}
		      \item{\(y=\frac{6}{7}x-4\)}
		      \item{\(y=\frac{-6}{7}x+4\)}
		      \item{\(y=\frac{6}{7}x+4\)}
		      \item{\(y=\frac{-6}{7}x-4\)}
	      \end{enumerate}

	      Answer: \(y=\frac{-6}{7}x-4\)}
	\item {Trevon is going to buy a coat and a hat. The coat costs $3$ times as much as the hat. He must spend less than $\$94$. Write an equation to express this situation (1).

	      Hints:
	      \begin{enumerate}
		      \item {This should be an inequality.}
		      \item {Don't forget to include the price of the hat.}
	      \end{enumerate}

	      Answer: \(4x < 94\)}
	\item {What represents the solution set to \(2x - 3y\geq5\) (1)?

	      Hints:
	      \begin{enumerate}
		      \item {Solve for y, and everything will make a lot more sense.}
	      \end{enumerate}

	      Answer: Show a few different inequalities to the student. Ask them what matches the given equation.}
	\item {Cell phone provider A charges $\$60$ a month for $1$ gigabyte (GB) of data plus $\$0.05$ for each megabyte (MB) of overage data. Cell phone provider B charges $\$45$ a month for $1$ GB of data plus $\$0.10$ for each MB of overage data. Assuming there will be data overage, how many MB of overage data would make the cost of both data plans the same (1)?

		      Hints:
		      \begin{enumerate}
			      \item {What is overage data?}
			      \item {Make an equation for provider A and B.}
			      \item {What is the slope and y-intercept for each equation?}
			      \item {What is the solution in the context of the equation?}
		      \end{enumerate}

		      Answer: $300$
	      }
	\item {The equation \(-x-2y=0\) is graphed in the $xy$ plane. Which of the following is a true statement about the graph?

	      \begin{enumerate}
		      \item {The graph goes through the point $(-1,2)$}
		      \item {The graph has a slope of 2}
		      \item {The graph goes through the point $(0,0)$}
		      \item {The graph has a slope of \(\frac{1}{2}\)}
	      \end{enumerate}

	      Answer: c
	      }

	\item {
	      Which of the ordered pairs $(x,y)$ satisfies the system of inequalities (1)?
	      \[
		      \begin{array}{l}
			      \begin{cases}
				      y \geq -1 & \\
				      y \leq 4x + 1
			      \end{cases}
		      \end{array}\]

	      \begin{enumerate}
		      \item{$(-4,2)$}
		      \item{$(0,4)$}
		      \item{$(2,-2)$}
		      \item{$(2,4)$}
	      \end{enumerate}

	      Hints:
	      \begin{enumerate}
		      \item{Enter both equations into Desmos}
	      \end{enumerate}

	      Answer: $(-4,2)$
	      }

	\item {Fabio and Carlos play on a basketball team together. In the last game, Fabio had $7$ points less than $2$ times as many points as Carlos. Fabio scored $31$ points in the game. How many points did Carlos score in the last game (1)?

	      Hints:
	      \begin{enumerate}
		      \item {Try making a few equations with the given information. \(\text{Fabio}=F\text{ and Carlos}=C\)}
		      \item {One of the equations is \(F=31\)}
		      \item {Another equation could be \(F=2*C-7\)}
	      \end{enumerate}
	      }



\end{enumerate}

\section{Credits}
\begin{enumerate}

	\item{
	      \href{https://www.khanacademy.org/test-prep/v2-sat-math/x0fcc98a58ba3bea7:algebra-medium}{Khan Academy, Digital SAT Math, Unit 6}}

\end{enumerate}
\end{document}
