\documentclass{article}
\usepackage{graphicx}
\usepackage{parskip}
\usepackage{hyperref}
\usepackage{amsmath}

\begin{document}
\section{General Algebra Problems}

\begin{enumerate}

	\item{Given the equation $\frac{1}{4}v=2+3$, what is the value of $6v-17+18-19+20$ (1)?

	      Hints:
	      \begin{enumerate}
		      \item{Solve for $v$ in the first equation, and plug $v$ in to the second equation with a calculator.}
	      \end{enumerate}

	      Answer: 122}
	\item {Given the system of equations:
	      \[
		      \begin{array}{l}
			      \begin{cases}
				      $-2x+by=59$ & \\
				      $5x-y=1$
			      \end{cases}
		      \end{array}\]
	      If the system of equations has exactly one solution $(x,y)$ and $x=2$, what is the value of $b$ (1)?

	      Hints:
	      \begin{enumerate}
		      \item{$x$ must be 2. Can you plug that in to the equation and solve for $y$, and consequently $b$ (substitution)?}
		      \item{Alternatively, plug the equation in on Desmos and add a slider for $b$. Change the slider until there is exactly one solution.}
	      \end{enumerate}

	      Answer: 7
	      }

	\item {The equation $8x-6y=1$ is graphed in the $xy$-plane. What is the slope of the line (1)?

	      Hints:
	      \begin{enumerate}
		      \item{Solve for $y$ (put the equation in point-slope form)}
	      \end{enumerate}

	      Answer: $\frac{4}{3}$}
	\item {Given the system of equations:
	      \[
		      \begin{array}{l}
			      \begin{cases}
				      $-x+3=y$ & \\
				      $-6x+18=6y$
			      \end{cases}
		      \end{array}\]
	      What are the solutions to the system of equations (1)?

	      Hints:
	      \begin{enumerate}
		      \item{What is a solution to a system of equations?}
		      \item {Graph the equation.}
	      \end{enumerate}

	      Answer: There are infinitely many solutions.
	      }

	\item {A line that slopes down and intercepts the $y$ axis when $y$ is less than $0$ is graphed in the $xy$ plane. What is the equation of the line (1)?

	      Answer choices:
	      \begin{enumerate}
		      \item{\(y=\frac{6}{7}x-4\)}
		      \item{\(y=\frac{-6}{7}x+4\)}
		      \item{\(y=\frac{6}{7}x+4\)}
		      \item{\(y=\frac{-6}{7}x-4\)}
	      \end{enumerate}

	      Hints:
	      \begin{enumerate}
		      \item{What form of linear equations are all these equations in?}
		      \item {What does negative slope/negative $y$ intercept look like in this form of linear equation?}
	      \end{enumerate}

	      Answer: \(y=\frac{-6}{7}x-4\)}
	\item {The equation \(-x-2y=0\) is graphed in the $xy$ plane. Which of the following is a true statement about the graph (1)?

	      \begin{enumerate}
		      \item {The graph goes through the point $(-1,2)$}
		      \item {The graph has a slope of 2}
		      \item {The graph goes through the point $(0,0)$}
		      \item {The graph has a slope of \(\frac{1}{2}\)}
	      \end{enumerate}

	      Hints:
	      \begin{enumerate}
		      \item{Graph the equation in Desmos and see which one of these answer choices is correct.}
	      \end{enumerate}

	      Answer: c
	      }

	\item {
	      Which of the ordered pairs $(x,y)$ satisfies the system of inequalities (1)?
	      \[
		      \begin{array}{l}
			      \begin{cases}
				      y \geq -1 & \\
				      y \leq 4x + 1
			      \end{cases}
		      \end{array}
	      \]

	      \begin{enumerate}
		      \item{$(-4,2)$}
		      \item{$(0,4)$}
		      \item{$(2,-2)$}
		      \item{$(2,4)$}
	      \end{enumerate}

	      Hints:
	      \begin{enumerate}
		      \item{Enter both equations into Desmos}
	      \end{enumerate}

	      Answer: $(-4,2)$
	      }


	\item {
	      Which of the following is true of the graph of

	      \(
	      \frac{y}{9} - \frac{x}{6} = 1
	      \)

	      in the $xy$-plane (1)?


	      \begin{enumerate}
		      \item (A) The graph's \(x\)-intercept is \(-6\) and its \(y\)-intercept is \(9\).
		      \item (B) The graph's \(x\)-intercept is \(9\) and its \(y\)-intercept is \(-6\).
		      \item (C) The graph is a line with a slope of \(\frac{2}{3}\).
		      \item (D) The graph is a line with a slope of \(-\frac{3}{2}\).
	      \end{enumerate}

	      Hints:
	      \begin{enumerate}
		      \item{Graph the equation}
	      \end{enumerate}

	      Answer: A
	      }
	\item {The equation \(2y-7x=5\) is graphed on the $xy$-plane. What is the slope of the line (1)?

	      Answer: \(\frac{7}{2}\)}

	\item {Given the equation \(17+27=-7w\), what is the value of \(10(-21w+1)\) (1)?

	      Hints:
	      \begin{enumerate}
		      \item {Solve for $w$ in the first equation. $w$ will not be a whole number (this is a great opportunity to clarify your work!)}
		      \item {Plug $w$ into the second equation and solve with a calculator.}
	      \end{enumerate}

	      Answer: 1330}
	\item {What represents the solution set to \(2x - 3y\geq5\) (1)?

	      Hints:
	      \begin{enumerate}
		      \item {Solve for y, and everything will make a lot more sense.}
	      \end{enumerate}

	      Answer: Show a few different inequalities to the student. Ask them what matches the given equation.}

	\item {In the following system of equations, $c$ is a constant. For what value of $c$ does the system of linear equations have infinitely many solutions (1)?

	      \[
		      \begin{array}{l}
			      \begin{cases}
				      x=-(3-cy)+6-7x & \\
				      3x-y=\frac{3}{2}-x
			      \end{cases}
		      \end{array}
	      \]

	      Hints:
	      \begin{enumerate}
		      \item{What does it look like when a system of equations has infinite solutions?}
		      \item{You can either graph this with Desmos, or solve it manually.}
		      \item{If you are solving it manually, put the equations in the same form (standard form or point-slope form) and see where $c$ slots in.}
	      \end{enumerate}

	      Answer: 2}

	\item{Which of the following accurately describes all solutions to the system of equations shown (1)?
	      \[
		      \begin{array}{l}
			      \begin{cases}
				      3x+2y=4(x-y-6) & \\
				      6(y+x)=7x-24
			      \end{cases}
		      \end{array}
	      \]

	      \begin{enumerate}
		      \item{$x=3$ and $y=-1$}
		      \item{$x=12$ and $y=-2$}
		      \item{There are infinite solutions to the system}
		      \item{There are no solutions to the system}
	      \end{enumerate}

	      Hints:
	      \begin{enumerate}
		      \item{I recommend that you graph this and solve it with Desmos}
	      \end{enumerate}

	      Answer: C
	      }
	\item{A line passes through a point $(3,2)$, and has a slope of $-\frac{1}{2}$. Write an equation that satisfies these requirements.

	      Hints:
	      \begin{enumerate}
		      \item{Use point slope form}
	      \end{enumerate}

	      Answer (unsimplified): \(y-2=-\frac{1}{2}(x-3)\)
	      }
	\item{Given the system of equations (1):
	      \[
		      \begin{array}{l}
			      \begin{cases}
				      1.5a-4.5b=3(a+b) & \\
				      5.5b=5(b-a)+2.5a
			      \end{cases}
		      \end{array}
	      \]
	      If $(a,b)$ is the solution to this system of equations, then what is the value of $b-a$?

	      Hints:
	      \begin{enumerate}
		      \item{This is just like any other system of equations that you might see}
		      \item{Think of $a$ as $x$ and $b$ as $y$}
		      \item{Either graph or solve by hand}
	      \end{enumerate}

	      Answer: 0
	      }

	\item{Consider this system of equations:
	      \[
		      \begin{array}{l}
			      \begin{cases}
				      11e-9f+1=5(f-3e) & \\
				      2f+4e=3
			      \end{cases}
		      \end{array}
	      \]

	      Which of the following statements is true (1)?

	      Hints:
	      \begin{enumerate}
		      \item{Graph on Desmos or substitute}
		      \item{If you choose to graph on Desmos, make sure you set $E=x$ and $F=y$, or vice versa}
		      \item{The units do not matter in this problem, as they are not specified}
	      \end{enumerate}

	      \begin{enumerate}
		      \item{There is only one solution, $(e,f)$, and $e*f$ is positive}
		      \item{There is only one solution, $(e,f)$, and $e*f$ is negative}
		      \item{There are infinitely many solutions}
		      \item{There are no solutions}
	      \end{enumerate}

	      Answer: A
	      }

	\item {Given a system of inequalities:

	      \[
		      \begin{array}{l}
			      \begin{cases}
				      y\geq-\frac{5}{2}x+1 & \\
				      y\leq-\frac{1}{2}x+\frac{5}{2}
			      \end{cases}
		      \end{array}
	      \]

	      If graphed in the $xy$ plane, which quadrant contains no solutions to the system (1)?

	      Hints:
	      \begin{enumerate}
		      \item{Quadrants go counter clockwise, starting from the right.}
	      \end{enumerate}

	      Answer: Quadrant III
	      }

	\item {Solve the following linear inequality by hand:
	      \(-5x+4\geq-3x-(5-x)\)

	      Answer: $x=1$}

	\item {Graph the following equation in the $xy$ plane. What is true about the graph (1)?

	      \(3x-2y=4\)

	      Answer(s): \begin{enumerate}
		      \item{The graph has a $y$ intercept at $y=-2$}
		      \item{The graph has an $x$ intercept at $x=\frac{4}{3}$}
		      \item{The graph has a slope of $\frac{3}{2}$}
	      \end{enumerate}}

	\item {In this system of inequalities, $a$ is a constant. If $(1,2)$ is a solution to the system, what is a possible value of $a$?

	      \[
		      \begin{array}{l}
			      \begin{cases}
				      ax+3y \geq 7 & \\
				      2y \leq ax+2
			      \end{cases}
		      \end{array}
	      \]

	      Hints:
	      \begin{enumerate}
		      \item{Graph this on Desmos, and use a slider to adjust the value of $a$}
	      \end{enumerate}

	      Answer: 2
	      }

	\item {Which of the following best describes the solution to the inequality shown (1)?

	      \(7x+1<x+9\)

	      Answer: $x<\frac{4}{3}$
	      }

	\item{If \(2+7z=-z-4\), what is the value of $z$?

	      Answer: $-\frac{3}{4}$}

\end{enumerate}

\section{Credits}
\begin{enumerate}

	\item{
	      \href{https://www.khanacademy.org/test-prep/v2-sat-math/x0fcc98a58ba3bea7:algebra-medium}{Khan Academy, Digital SAT Math, Unit 6}}

\end{enumerate}
\end{document}
